Measurement Bias from Address Aliasing

### 2016-01-09 paper.tex
Shortend header.

In general, any change to how data is laid out in memory layout can potentially introduce bias effects from address aliasing.
Analyzing an example with bias to environment size, we determined that collisions between automatic variables and static data resulted in aliasing for certain stack positions.
Aliasing conditions were triggered because variations in environment size offset the virtual addresses of stack allocated variables.
Dynamically allocated data is controlled by heap allocators, which we introduce as another source of bias.
Comparing four different libraries, we show that most implementations tend to favor page alignment for larger requests.
This means that structures such as vectors and matrices are likely to alias by default, which can be worst case scenarios for many algorithms.
%Address aliasing can have significant performance impact for algorithms operating on heap allocated buffers, which 
We analyze an example with up to $2x$ variation in cycle count between different heap alignments, showing that address aliasing can have a significant performance impact.
We are able to identify instances of alias issues in matrix-vector multiplication routines for different BLAS libraries, proving that this phenomenon also appear in real, performance critical code.

>>>>

In general, any change to how data is laid out in memory layout can potentially introduce bias effects from address aliasing.
Analyzing an example with bias to environment size, we determined that collisions between automatic variables and static data resulted in aliasing for certain stack positions.
Aliasing conditions were triggered because variations in environment size offset the virtual addresses of stack allocated variables.
Dynamically allocated data is controlled by heap allocators, which we introduce as another source of bias.
Comparing four different libraries, we show that most implementations tend to favor page alignment for larger requests.
This means that structures such as vectors and matrices are likely to alias by default, which can be worst case scenarios for many algorithms.
%Address aliasing can have significant performance impact for algorithms operating on heap allocated buffers, which 
We analyze an example with up to $2x$ variation in cycle count between different heap alignments, showing that address aliasing can have a significant performance impact.
We are able to identify instances of alias issues in matrix-vector multiplication routines for different BLAS libraries, showing that this effect also appears in real, performance critical code.
